Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/fig-motivation.tex
Figure

\begin{figure}
\begin{tabular}{@{}llll @{}}
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
  Memory corruption\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: 2013-5660, - 0742, -0138, 2012-4987, -1163,-1162, 2011-2265,
    2010-4535, -1657, -1336, -1218} & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Compressor uses weak cryptography, even if the user
  selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related .zip processing }& \bf 16  \\  
  Mishandling archive contents &  2012-4389 & A web application overwrites .htaccess files and
  executable files by extracting uploaded .ZIP files to a publicly accessible folder  & 25\\
   Unrelated to .zip &2011-3371& Vulnerability leaking postal Zip codes & 42\\
  \multicolumn{3}{l}{\bf Total vulnerabilities} & \bf 83\\

\end{tabular}
\caption{Classification of known vulnerabilities in the CVE database between 2010 and 2014 related to the search term ``ZIP''}
\label{fig:motivation} 
\end{figure}

>>>>

\begin{figure*}
\begin{tabular}{@{}llll @{}}
 \bf Classification & \bf Example CVE & \bf Example description & \bf Count\\
  Memory corruption\footnote{We classified the following vulnerabilities as memory corruption
    attacks based on their description: 2013-5660, - 0742, -0138, 2012-4987, -1163,-1162, 2011-2265,
    2010-4535, -1657, -1336, -1218} & 2013-5660 & Buffer overflow & 11\\
  Parser ambiguities & 2013-1462 & Multiple virus scanners interpret ZIP files incorrectly.& 4\\
  Semantic misunderstanding & 2014-2319 & Compressor uses weak cryptography, even if the user
  selects AES & 1\\
  \multicolumn{3}{l}{\bf Total vulnerabilities related to .zip processing }& \bf 16  \\  
  Mishandling archive contents &  2012-4389 & 
\begin{minipage}{7cm}
A web application overwrites .htaccess files and
  executable files by extracting uploaded .ZIP files to a publicly accessible folder  
\end{minipage}& 25\\
   Unrelated to .zip &2011-3371& Vulnerability leaking postal Zip codes & 42\\
  \multicolumn{3}{l}{\bf Total vulnerabilities} & \bf 83\\

\end{tabular}
\caption{Classification of known vulnerabilities in the CVE database between 2010 and 2014 related to the search term ``ZIP''}
\label{fig:motivation} 
\end{figure*}
